The Weakly Nonlinear Saturation of the Magnetorotational Instability

### 2014-09-10 paper/mri paper.tex
more and some tweaking

The destabilizing substitution is made, and Equations \ref{eqset1} - \ref{eqset4} are rewritten such that the fluid variables are contained in a state vector $\mathbf{V} = \left[\Psi, u_y, A, B\right]^\mathrm{T}$. This yields the following system of equations.

@@

>>>>

The destabilizing substitution is made, and Equations \ref{eqset1} - \ref{eqset4} are rewritten such that the fluid variables are contained in a state vector $\mathbf{V} = \left[\Psi, u_y, A, B_y\right]^\mathrm{T}$. This yields the following system of equations.

@@

\beq
\Psi = \partial_x \Psi = u_y = A = \partial_x B_y = 0
\eeq

The practical advantage of our ansatz construction (Equation \ref{V1_ansatz}) is clear: the separable x-dependence means that the radial boundary conditions are solved in only one dimension. Thus our analytical framework is able to side-step many of the resolution issues faced by multidimensional simulations. We are able to resolve even significant structure in the boundary layers of our domain, because we need only resolve it in one dimension.
